Short and Mechanized Logical Relation for Dependent Type Theory

### 2024-02-23 paper/paper.tex
Minor

\section{Existence of $\beta$-normal forms}
\label{sec:extension}
In this section, we sketch out how the logical relation from
Section~\ref{sec:logreldep} can be extended to show the existence of
$\beta$ normal forms for (open and closed) well-typed terms.
\scw{Why is this a sketch? We've done the whole proof and we will
explain it all, right?}

>>>>

\section{Existence of $\beta$-normal forms}
\label{sec:extension}
In this section, we show how the logical relation from
Section~\ref{sec:logreldep} can be extended to show the existence of
$\beta$ normal forms for (open and closed) well-typed terms.
\scw{Why is this a sketch? We've done the whole proof and we will
explain it all, right?}\yl{s/sketch out/show. I used sketch because we
didn't spell out the full proofs}
